From Principles to Practice with Class in the First Year

### 2013-04-13 tfpie/tfpie.tex
start on context

>>>>

At Northeastern, the College of Computer \& Information Science
requires a four course introductory sequence in the first year.  The
first semester features both a course on discrete mathematics as well
as an introduction to programming following the \emph{How to Design
  Programs} curriculum.  The second semester follows with a course on
object-oriented programming and one featuring formal reasoning about
programs, both on paper and with the ACL2 theorem prover.

Subsequent to the first year, students take a wide variety of
follow-up courses, ranging from a required course in ``Object-oriented
design'' to architecture, operating systems, robotics, and programming
languages.  No standard language is used in these courses.

More significantly, Northeastern distinctively emphasizes experiential
education, with almost all Computer Science majors participating in a
6 month ``co-op'' internship after their third semester.  These co-ops
take place at a wide variety of companies, and while most students do
some software development, there is almost no uniformity beyond that.
